### 2014-06-19 ms/ms.Rmd
Work on paper, citations. #119

# library(pander)

@@

Quantifying the amount of mass or energy invested in plant tissues is of fundamental interest across a range of disciplines, including ecology, forestry, ecosystem science, and climate change science `r citep(c(Falster2011="10.1111/j.1365-2745.2010.01735.x"))`. The allocation of net primary production into different plant components is an important process affecting the lifetime of carbon in ecosystems, and resource use and productivity by plants. While many studies in have destructively harvested woody plants in the name of science, most of these data have only been made available in the form of summary tables or figures included in publications, or as totals for a forest plot. Until now, much of the raw data resides piecemeal on the hard drives of individual scientists spread around the world.

Several studies have gathered together the fitted (allometric) equations for separate datasets, yet few have attempted to organize and share the raw individual plant data underpinning these equations. Gathered together, such data would be invaluable and represent an important resource for the community.

@@

Combining data from many different studies, each using its own set of terms and units, and quirks, is no trivial task `r citep(c(Michener1997="10.1890/1051-0761(1997)007[0330:NMFTES]2.0.CO;2", Kandel2011="10.1145/1978942.1979444"))`. This compilation would not have been possible without several new technologies. In particular,

@@

Until recently, scientific publications in biology have mostly been concerned with "small data" `r citep(c(VanNoorden2013="10.1038/nj7461-243a"))`. Datasets arrive in small parcels, corresponding to the work of an individual study, or perhaps a handful of studies. It is exciting to be able to put these parcels together, to create something larger. We hope other people will use this dataset and build on it. See [https://github.com/dfalster/baad](https://github.com/dfalster/baad) for information on how to contribute to future releases.

@@

**Latest update**: xx for all data files.

@@

**Data verification**:

@@

Identity:
Size:
Format and storage mode: ASCII text, comma delimited. Missing values
are denoted as 'NA'.
Header information:

@@

### C. Number of observations by variable

>>>>

bib <- read.bibtex("refs.bib")

@@

Quantifying the amount of mass or energy invested in plant tissues is of fundamental interest across a range of disciplines, including ecology, forestry, ecosystem science, and climate change science `r citep(c("10.1111/j.1365-2745.2010.01735.x"))`. The allocation of net primary production into different plant components is an important process affecting the lifetime of carbon in ecosystems, and resource use and productivity by plants. While many studies in have destructively harvested woody plants in the name of science, most of these data have only been made available in the form of summary tables or figures included in publications. Until now, the raw data has resided piecemeal on the hard drives of individual scientists spread around the world. Several studies have gathered together the fitted (allometric) equations for separate datasets `r citep(c("10.3832/ifor0901-006","10.1016/S0378-1127(97)00019-4"))`, `citep(bib["zianis_biomass_2005"])`, but none have previously attempted to organize and share the raw individual plant data underpinning these equations on a large scale. Gathered together, such data would represent an important resource for the community, meeting a widely recognised need for rich, open data resources to solve ecological problems `r citep(c("10.1007/s13595-014-0375-3","10.1038/505160a", "10.1016/j.tree.2013.05.002"))`.

@@

Combining data from many different studies, each using its own set of terms and units, and quirks, is no trivial task `r citep(c("10.1890/1051-0761(1997)007[0330:NMFTES]2.0.CO;2","10.12688/f1000research.4518"))`. This compilation would not have been possible without several new technologies. In particular,

@@

Until recently, scientific publications in biology have mostly been concerned with "small data" `r citep("10.1038/nj7461-243a")`. Datasets arrive in small parcels, corresponding to the work of an individual study, or perhaps a handful of studies. It is exciting to be able to put these parcels together, to create something larger. We hope other people will use this dataset and build on it. See [https://github.com/dfalster/baad](https://github.com/dfalster/baad) for information on how to contribute to future releases.

@@

**Latest update**: xxxx for all data files.

@@

**Data verification**: Data have passed through several rounds of review: i) initial analysis by data contributors, ii) Review by compilers of database, iii) Additional review by contributors using automated reports provided in XXXXX.

@@

Identity:
Size:
Format and storage mode: ASCII text, comma delimited. Missing values
are denoted as 'NA'.

@@

**Number of observations by variable**
